---
title: "Student Success Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT, #for better tables
               ggplot
               )

df = read_csv("clean_data.csv")
companies = read_csv("top_companies.csv")
```

# Overview and Insights {data-orientation=columns}

## Column {data-width=500}

### Project/Problem Overview

Kirk Bogard and the team at the Office of the Dean & External Relations is responsible for building relationships and securing funding for the FSB program. Some pain points for Kirk and his team include the presence of unstructured data, which necessitated extensive cleaning before meaningful analysis could commence. Additionally, there was a clear lack of understanding regarding the changing trends in student placement and salary over time. This gap in knowledge posed significant hurdles, especially when trying to discern the performance of FSB starting salaries across different majors.

### Our Solution

To alleviate some of the difficulties Kirk faced as well as provide Kirk with ready-to-use data and visualizations, we devised comprehensive solution:

Data Cleaning: We started with the data cleaning processes to transform the raw data into a usable format. This ensured that only relevant variables were considered, paving the way for accurate analysis.

Our approach leaned heavily on data visualization:

*We created histograms that detail the salary distribution for each specific major on a yearly basis, providing a clear view of evolving trends.

*Bar charts were formulated to compare the starting salaries offered by top companies to FSB majors, shedding light on industry preferences and biases.

*Comparative Analysis: To offer a broader perspective, we juxtaposed FSB's data with average starting salaries from Fisher School of Business and Kelley School of Business. This allowed us to benchmark FSB's performance across various majors in comparison to other top business schools in the area. 

## Column {data-width=500}

### Insights and Conclusions

1. Information Systems and Business Analytics majors tend to make the highest salaries, with Finance and Economics trailing slightly behind. The average salary for Management and Leadership majors took a big dip in 2021 to be the lowest paying major, going from just over 58,000 dollars in 2020 to under 51,000 dollars in 2021.

2. When comparing Farmer with Kelley School of Business and Fisher School of Business, we see that Kelley outperforms the other schools for all majors. Farmer and Fisher go back and forth for majors but are roughly the same.

3. For the majority of majors, both median and average salaries have risen from the time frame of 2019 to 2021.

4. For top companies, Information Systems majors tend to make the highest average starting salaries. 

### Links

Indiana University Salaries: https://kelley.iu.edu/recruiters-companies/undergrad/statistics/salary-statistics/index.html

Ohio State Salaries: https://files.fisher.osu.edu/careers-recruiting/public/2021-10/AnnualReport2021.pdf?VersionId=UnbXIIgZenGaz8EVfozFCS1lJrl9bf5A

CPI Inflation Calculator: 
https://www.officialdata.org/us/inflation/2022?endYear=2021&amount=60000

# Major Salaries by Year {data-orientation=columns}

## Column {data-width=333}

###

```{r, fig.width = 4, fig.height=2.5, echo=FALSE}
# Finance Major
finance_data <- df[df$major1 == "Finance", ]
plot <- ggplot(finance_data, aes(x = survey_salary)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "blue") +
  facet_wrap(~year.x, scales = "fixed") +
  labs(
    title = "Histogram of Finance Major Salaries",
    x = "Salary",
    y = "Frequency"
  ) +
  scale_x_continuous(limits = c(0, 100000)) +  # Set the x-axis range up to 100,000
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

interactive_plot <- ggplotly(plot)
interactive_plot
```

###

```{r, fig.width = 4, fig.height=2.5, echo=FALSE}
analytics_data <- df[df$major1 == "Business Analytics", ]

plot <- ggplot(analytics_data, aes(x = survey_salary)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "blue") +
  facet_wrap(~year.x, scales = "fixed") +
  labs(
    title = "Histogram of Business Analytics Major Salaries",
    x = "Salary",
    y = "Frequency"
  ) +
  scale_x_continuous(labels = scales::number_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

interactive_plot <- ggplotly(plot)
interactive_plot
```

###

```{r, fig.width = 4, fig.height=2.5, echo=FALSE}
economics_data <- df[df$major1 == "Business Economics", ]
plot <- ggplot(economics_data, aes(x = survey_salary)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "blue") +
  facet_wrap(~year.x, scales = "fixed") +
  labs(
    title = "Histogram of Economics Major Salaries",
    x = "Salary",
    y = "Frequency"
  ) +
  scale_x_continuous(labels = scales::number_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

interactive_plot <- ggplotly(plot)
interactive_plot
```

## Column {data-width=333}

###

```{r, fig.width = 4, fig.height=2.5, echo=FALSE}
marketing_data <- df[df$major1 == "Marketing", ]
plot <- ggplot(marketing_data, aes(x = survey_salary)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "blue") +
  facet_wrap(~year.x, scales = "fixed") +
  labs(
    title = "Histogram of Marketing Major Salaries",
    x = "Salary",
    y = "Frequency"
  ) +
  scale_x_continuous(labels = scales::number_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

interactive_plot <- ggplotly(plot)
interactive_plot
```

###

```{r, fig.width = 4, fig.height=2.5, echo=FALSE}
entre_data <- df[df$major1 == "Entrepreneurship", ]

plot <- ggplot(entre_data, aes(x = survey_salary)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "blue") +
  facet_wrap(~year.x, scales = "fixed") +
  labs(
    title = "Histogram of Entrepreneurship Major Salaries",
    x = "Salary",
    y = "Frequency"
  ) +
  scale_x_continuous(labels = scales::number_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

interactive_plot <- ggplotly(plot)
interactive_plot
```

### 

```{r, fig.width = 4, fig.height=2.5, echo=FALSE}
supply_data <- df[df$major1 == "Supply Chain & Operations Mgmt", ]

plot <- ggplot(supply_data, aes(x = survey_salary)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "blue") +
  facet_wrap(~year.x, scales = "fixed") +
  labs(
    title = "Histogram of Supply Chain Major Salaries",
    x = "Salary",
    y = "Frequency"
  ) +
  scale_x_continuous(labels = scales::number_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

interactive_plot <- ggplotly(plot)
interactive_plot
```

## Column {data-width=333}

###

```{r, fig.width = 4, fig.height=2.5, echo=FALSE}
accountancy_data <- df[df$major1 == "Accountancy", ]

plot <- ggplot(accountancy_data, aes(x = survey_salary)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "blue") +
  facet_wrap(~year.x, scales = "fixed") +
  labs(
    title = "Histogram of Accountancy Major Salaries",
    x = "Salary",
    y = "Frequency"
  ) +
  scale_x_continuous(labels = scales::number_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

interactive_plot <- ggplotly(plot)
interactive_plot
```

###

```{r, fig.width = 4, fig.height=2.5, echo=FALSE}
mgmt_data <- df[df$major1 == "Management and Leadership", ]

plot <- ggplot(mgmt_data, aes(x = survey_salary)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "blue") +
  facet_wrap(~year.x, scales = "fixed") +
  labs(
    title = "Histogram of Management and Leadership Major Salaries",
    x = "Salary",
    y = "Frequency"
  ) +
  scale_x_continuous(labels = scales::number_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

interactive_plot <- ggplotly(plot)
interactive_plot
```

###

```{r, fig.width = 4, fig.height=2.5, echo=FALSE}
information_data <- df[df$major1 == "Information Systems", ]

plot <- ggplot(information_data, aes(x = survey_salary)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "blue") +
  facet_wrap(~year.x, scales = "fixed") +
  labs(
    title = "Histogram of Information Systems Major Salaries",
    x = "Salary",
    y = "Frequency"
  ) +
  scale_x_continuous(labels = scales::number_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

interactive_plot <- ggplotly(plot)
interactive_plot
```

###

```{r, fig.width = 4, fig.height=2.5, echo=FALSE}
human_data <- df[df$major1 == "Human Capital Mgmt& Leadership", ]

plot <- ggplot(human_data, aes(x = survey_salary)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "blue") +
  facet_wrap(~year.x, scales = "fixed") +
  labs(
    title = "Histogram of Human Capital Management Major Salaries",
    x = "Salary",
    y = "Frequency"
  ) +
  scale_x_continuous(labels = scales::number_format(scale = 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

interactive_plot <- ggplotly(plot)
interactive_plot
```
# FSB {data-orientation=columns}

## Column {data-width=400}

### Farmer's Average Salries by Major by Year

```{r,echo=FALSE}
result <- df %>%
  group_by(major1, year.x) %>%
  summarise(average_salary = mean(survey_salary, na.rm = TRUE)) %>%
  ungroup()

plotly_chart <- result %>%
  plot_ly(x = ~factor(year.x), y = ~average_salary, color = ~major1, type = "scatter", mode = "lines") %>%
  layout(
    xaxis = list(title = "Year"),
    yaxis = list(title = "Average Salary"),
    showlegend = TRUE
  )

plotly_chart
```

### FSB's Salaries as a Whole by Year

```{r,echo=FALSE}
x_axis_range <- c(0, 100000)  # Used 100,000 to get a more accurate look of the shape of the histogram

interactive_plot <- plot_ly(df, x = ~survey_salary, type = "histogram", 
                            xbins = list(start = x_axis_range[1], end = x_axis_range[2], size = 5000),
                            marker = list(color = "blue", line = list(color = "black", width = 1)), autobinx = FALSE) %>%
  layout(
    title = "Histogram of FSB Salaries by Year",
    xaxis = list(title = "Salary"),
    yaxis = list(title = "Frequency"),
    bargap = 0  # Set bargap to 0 to have only one bar per bin
  )
interactive_plot
```


## Column {data-width=600}

### Comparable School's Average Salaries

```{r,echo=FALSE}
## Creating data frame for comparison. 

school = c("Miami", "Miami", "Miami", "Miami","Miami", "Miami", "Indiana", "Indiana", "Indiana", "Indiana","Indiana", "Indiana", "Ohio State", "Ohio State", "Ohio State", "Ohio State", "Ohio State", "Ohio State")

major = c("Accounting", "Economics", "Marketing", "Finance", "Information Systems", "Operations Management", "Accounting", "Economics", "Marketing", "Finance", "Information Systems", "Operations Management", "Accounting", "Economics", "Marketing", "Finance", "Information Systems", "Operations Management")

salary = c(59243, 60760, 52110, 61855, 66616, 56470, 66071, 72032, 60524, 72705, 70816, 64478, 57281, 57794, 55179, 63161, 68445, 58271)

df = data.frame(School = school, Major = major, Salary = salary)

plot <- plot_ly(df, x = ~Major, y = ~Salary, type = 'bar', text = ~School, color = ~School) %>%
  layout(title = "Average Salary by Major and School",
         xaxis = list(title = "Major"),
         yaxis = list(title = "Average Salary"))

plot
```


# Salaries by Top Companies {data-orientation=columns}

## Column {data-width=500}

### Top 10 Companies
```{r,echo=FALSE}
data = companies %>%
  #filter(intern_status == "Yes") %>%
  #filter(pay_status == "Yes") %>%
  group_by(survey_company, year.x, major1, survey_salary) %>%
  summarize(count=n()) %>%
  arrange(survey_company, year.x, major1, survey_salary, -count)

#data$employer = fct_explicit_na(data$employer, "unkown")
#finding all NAs and putting it into "unknown" category


datatable(data, rownames=F, extensions = "Buttons", 
          options =list(dom = "Bfrtip",
                        buttons=c("copy", "csv", "excel")
                        ),
          filter = list(position = "bottom",
                        clear=F,plain= T
                        )
          )
```

### Deloitte Average Salaries

```{r, echo =FALSE, fig.width = 8, fig.height=6}
#Deloitte Bar Chart

filtered_data <- companies %>%
  filter(survey_company == "DELOITTE") %>%
  group_by(major1, survey_company) %>%
  summarise(average_salary = mean(survey_salary))

# Create a responsive plotly bar chart for "DELOITTE"
plot_ly(filtered_data, x = ~major1, y = ~average_salary, type = "bar", marker = list(color = "blue")) %>%
  layout(xaxis = list(title = "Major"),
         yaxis = list(title = "Average Salary", range = c(0, 80000)),
         barmode = "group")

```

## Column {data-width=500}

### EY Average Salaries

```{r, echo = FALSE, fig.width = 4, fig.height=2.5}
#EY

filtered_data <- companies %>%
  filter(survey_company == "EY") %>%
  group_by(major1, survey_company) %>%
  summarise(average_salary = mean(survey_salary))

# Create a responsive plotly bar chart for "EY"
plot_ly(filtered_data, x = ~major1, y = ~average_salary, type = "bar", marker = list(color = "blue")) %>%
  layout(xaxis = list(title = "Major"),
         yaxis = list(title = "Average Salary", range = c(0, 80000)),
         barmode = "group")
```

### Textron Average Salries

```{r, echo = FALSE, fig.width = 4, fig.height=2.5}
#Textron Bar Chart

filtered_data <- companies %>%
  filter(survey_company == "TEXTRON") %>%
  group_by(major1, survey_company) %>%
  summarise(average_salary = mean(survey_salary))

# Create a responsive plotly bar chart for "TEXTRON"
plot_ly(filtered_data, x = ~major1, y = ~average_salary, type = "bar", marker = list(color = "blue")) %>%
  layout(xaxis = list(title = "Major"),
         yaxis = list(title = "Average Salary", range = c(0, 80000)),
         barmode = "group")

```

```{r}
sessionInfo()
```




