---
title: "Student Success Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )

df = read_csv("clean_data.csv")
companies = read_csv("top_companies.csv")
```

# Overview and Insights {data-orientation=columns}

## Column {data-width=500}

### Project/Problem Overview

Show salaries of Farmer students.

### Our Solution

We will create histograms.

## Column {data-width=500}

### Insights and Conclusions

### Links

# Major Salaries by Year {data-orientation=columns}

## Column {data-width=400}

### Salary Distribution per Major by Year (Histograms)

```{r,echo=FALSE}
print(df)
```

# FSB {data-orientation=columns}

## Column {data-width=400}

### Average Salary of Majors by Year (Line Chart)

```{r,echo=FALSE}

```

### National Average Salary of Majors by Year (Line Chart)

```{r,echo=FALSE}

```


## Column {data-width=600}

### Salary Distribution by Year of FSB as a Whole (Histograms)

```{r,echo=FALSE}

```


# Salaries by Top Companies {data-orientation=columns}

## Column {data-width=500}

### Table of Top 10 Companies (columns include: company, major, salary, and year)

```{r,echo=FALSE}
data = companies %>%
  #filter(intern_status == "Yes") %>%
  #filter(pay_status == "Yes") %>%
  group_by(survey_company, year.x, major1, survey_salary) %>%
  summarize(count=n()) %>%
  arrange(survey_company, year.x, major1, survey_salary, -count)

#data$employer = fct_explicit_na(data$employer, "unkown")
#finding all NAs and putting it into "unknown" category


datatable(data, rownames=F, extensions = "Buttons", 
          options =list(dom = "Bfrtip",
                        buttons=c("copy", "csv", "excel")
                        ),
          filter = list(position = "bottom",
                        clear=F,plain= T
                        )
          )
```

## Column {data-width=500}

### Average Salary of Each Major of the Top 3 Companies (Bar Chart)

```{r}

```

