---
title: "Student Success Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )

#read in data
#data=readRDS("FSB_BI_Survey_2019_2021.rds")
```

# Overview and Insights {data-orientation=columns}

## Column {data-width=500}

### Project/Problem Overview

### Our Solution

## Column {data-width=500}

### Insights and Conclusions

### Links

# Major Salaries by Year {data-orientation=columns}

## Column {data-width=400}

### Salary Distribution per Major by Year (Histograms)

```{r,echo=FALSE}

```

# FSB {data-orientation=columns}

## Column {data-width=400}

### Average Salary of Majors by Year (Line Chart)

```{r,echo=FALSE}

```

### National Average Salary of Majors by Year (Line Chart)

```{r,echo=FALSE}

```


## Column {data-width=600}

### Salary Distribution by Year of FSB as a Whole (Histograms)

```{r,echo=FALSE}

```


# Salries by Top Companies {data-orientation=columns}

## Column {data-width=500}

### Table of Top 10 Companies (columns include: company, major, salary, and year)

```{r,echo=FALSE}

```

## Column {data-width=500}

### Average Salary of Each Major of the Top 3 Companies (Bar Chart)

```{r}

```

